Active Learning for Level Set Estimation

### 2013-07-31 figurefactory/files/voned_cl_41_imp_2_poster.tex
Many small fixes

\begin{axis}[%
tick label style={font=\Huge},
label style={font=\Huge},
label shift={-4pt},
xlabel shift={-6pt},
xticklabel shift={5pt},
legend style={font=\Huge},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=2,
xtick={0, 0.5, 1, 1.5, 2},
ymin=-2, ymax=4,
tickwidth=0cm,
]

@@

line width=3.0pt,

@@

\addplot [
color=darkgray,
solid,
only marks,
mark=square*,
mark size=5pt,
forget plot
]
coordinates{
 %(0,-2)
 %(0.01,-2)
(0.023,-2)
(0.03,-2)(0.04,-2)(0.05,-2)(0.06,-2)(0.07,-2)(0.08,-2)(0.09,-2)(0.1,-2)(0.11,-2)(0.12,-2)(0.13,-2)(0.14,-2)(0.15,-2)(0.16,-2)(0.17,-2)(0.18,-2)(0.19,-2)(0.2,-2)(0.21,-2)(0.22,-2)(0.23,-2)(0.24,-2)(0.25,-2)(0.26,-2)(0.27,-2)(0.67,-2)(0.68,-2)(0.69,-2)(0.7,-2)(0.71,-2)(0.72,-2)(0.73,-2)(0.74,-2)(0.75,-2)(0.76,-2)(0.77,-2)(0.78,-2)(0.79,-2)(0.8,-2)(0.81,-2)(0.82,-2)(0.83,-2)(0.84,-2)(0.85,-2)(0.86,-2)(0.87,-2)(0.88,-2)(0.89,-2)(0.9,-2)(0.91,-2)(0.92,-2)(1.1,-2)(1.11,-2)(1.12,-2)(1.13,-2)(1.14,-2)(1.15,-2)(1.16,-2)(1.17,-2)(1.18,-2)(1.19,-2)(1.2,-2)(1.21,-2)(1.22,-2)(1.23,-2)(1.24,-2)(1.25,-2)(1.26,-2)(1.27,-2)(1.28,-2)(1.29,-2)(1.3,-2)(1.31,-2)(1.32,-2)(1.33,-2)(1.34,-2)(1.35,-2)(1.36,-2)(1.37,-2)(1.38,-2)(1.39,-2)(1.4,-2)(1.41,-2)(1.63,-2)(1.64,-2)(1.65,-2)(1.66,-2)(1.67,-2)(1.68,-2)(1.69,-2)(1.7,-2)(1.71,-2)(1.72,-2)(1.73,-2)(1.74,-2)(1.75,-2)(1.76,-2)(1.77,-2)(1.78,-2)(1.79,-2)(1.8,-2)(1.81,-2)(1.82,-2)(1.83,-2)(1.84,-2)(1.85,-2)(1.86,-2)(1.87,-2)(1.88,-2)(1.89,-2)(1.9,-2)(1.91,-2)(1.92,-2)(1.93,-2)(1.94,-2)(1.95,-2)(1.96,-2)(1.97,-2)
(1.977,-2)
%(1.99,-2)
 %(2,-2) 
};

\addplot [
color=red!40!yellow,
solid,
only marks,
mark=square*,
mark size=5pt,
forget plot
]
coordinates{
 (0.28,-2)(0.29,-2)(0.3,-2)(0.31,-2)(0.32,-2)(0.33,-2)(0.34,-2)(0.35,-2)(0.36,-2)(0.37,-2)(0.38,-2)(0.39,-2)(0.4,-2)(0.41,-2)(0.42,-2)(0.43,-2)(0.44,-2)(0.45,-2)(0.46,-2)(0.47,-2)(0.48,-2)(0.49,-2)(0.5,-2)(0.51,-2)(0.52,-2)(0.53,-2)(0.54,-2)(0.55,-2)(0.56,-2)(0.57,-2)(0.58,-2)(0.59,-2)(0.6,-2)(0.61,-2)(0.62,-2)(0.63,-2)(0.64,-2)(0.65,-2)(0.66,-2)(1.42,-2)(1.43,-2)(1.44,-2)(1.45,-2)(1.46,-2)(1.47,-2)(1.48,-2)(1.49,-2)(1.5,-2)(1.51,-2)(1.52,-2)(1.53,-2)(1.54,-2)(1.55,-2)(1.56,-2)(1.57,-2)(1.58,-2)(1.59,-2)(1.6,-2)(1.61,-2)(1.62,-2) 
};

\addplot [
color=locol,
solid,
only marks,
mark=square*,
mark size=5pt,
forget plot
]
coordinates{
 (0.93,-2)(0.94,-2)(0.95,-2)(0.96,-2)(0.97,-2)(0.98,-2)(0.99,-2)(1,-2)(1.01,-2)(1.02,-2)(1.03,-2)(1.04,-2)(1.05,-2)(1.06,-2)(1.07,-2)(1.08,-2)(1.09,-2) 
};

\addplot [
color=red,
dashed,
line width=3.0pt,
forget plot
]
coordinates{
 (0,1.2)(2,1.2)
};

\addplot [
color=black,
solid,
line width=3pt,
mark=-,
mark size=4pt,
forget plot
]
coordinates{
 (1.23,0.0268)(1.23,1.9195)
};

\addplot [
color=yellow,
solid,
line width=5pt,
forget plot
]
coordinates{
 (1.23,1.2)(1.23,1.9195)
};

\addplot [
color=black,
solid,
line width=3pt,
mark=-,
mark size=4pt,
forget plot
]
coordinates{
 (0.23,0.9288)(0.23,3.8259)
};

\addplot [
color=yellow,
solid,
line width=5pt,
forget plot
]
coordinates{
 (0.23,0.9288)(0.23,1.2)
};

>>>>

\begin{axis}[%
tick label style={font=\Huge},
label style={font=\Huge},
label shift={-4pt},
xlabel shift={-6pt},
legend style={font=\Huge},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=2,
xticklabel shift={5pt},
xtick={0, 0.5, 1, 1.5, 2},
ymin=-2, ymax=4,
tickwidth=0.1cm,
clip=false
]

@@

line width=3pt,

@@

\addplot [
color=darkgray,
solid,
only marks,
mark=square*,
mark size=5pt,
forget plot
]
coordinates{
 %(0,-2)
 %(0.01,-2)
(0.023,-2)
(0.03,-2)(0.04,-2)(0.05,-2)(0.06,-2)(0.07,-2)(0.08,-2)(0.09,-2)(0.1,-2)(0.11,-2)(0.12,-2)(0.13,-2)(0.14,-2)(0.15,-2)(0.16,-2)(0.17,-2)(0.18,-2)(0.19,-2)(0.2,-2)(0.21,-2)(0.22,-2)(0.23,-2)(0.24,-2)(0.25,-2)(0.26,-2)(0.27,-2)(0.28,-2)(0.29,-2)(0.30,-2)(0.31,-2)(0.32,-2)(0.33,-2)(0.34,-2)
(0.35,-2)(0.36,-2)(0.37,-2)
(0.59,-2)(0.6,-2)(0.61,-2)(0.62,-2)(0.63,-2)(0.64,-2)(0.65,-2)(0.66,-2)
(0.67,-2)(0.68,-2)(0.69,-2)(0.7,-2)(0.71,-2)(0.72,-2)(0.73,-2)(0.74,-2)(0.75,-2)(0.76,-2)(0.77,-2)(0.78,-2)(0.79,-2)(0.8,-2)(0.81,-2)(0.82,-2)(0.83,-2)(0.84,-2)(0.85,-2)(0.86,-2)(0.87,-2)(0.88,-2)(0.89,-2)(0.9,-2)(0.91,-2)(0.92,-2)(1.1,-2)(1.11,-2)(1.12,-2)(1.13,-2)(1.14,-2)(1.15,-2)(1.16,-2)(1.17,-2)(1.18,-2)(1.19,-2)(1.2,-2)(1.21,-2)(1.22,-2)(1.23,-2)(1.24,-2)(1.25,-2)(1.26,-2)(1.27,-2)(1.28,-2)(1.29,-2)(1.3,-2)(1.31,-2)(1.32,-2)(1.33,-2)(1.34,-2)(1.35,-2)(1.36,-2)(1.37,-2)(1.38,-2)(1.39,-2)(1.4,-2)
(1.41,-2)(1.42,-2)(1.43,-2)(1.44,-2)(1.45,-2)(1.46,-2)(1.47,-2)(1.48,-2)(1.49,-2)(1.5,-2)
(1.51,-2)(1.52,-2)(1.53,-2)(1.54,-2)(1.55,-2)(1.56,-2)(1.57,-2)(1.58,-2)(1.59,-2)(1.6,-2)(1.61,-2)(1.62,-2)
(1.63,-2)(1.64,-2)(1.65,-2)(1.66,-2)(1.67,-2)(1.68,-2)(1.69,-2)(1.7,-2)(1.71,-2)(1.72,-2)(1.73,-2)(1.74,-2)(1.75,-2)(1.76,-2)(1.77,-2)(1.78,-2)(1.79,-2)(1.8,-2)(1.81,-2)(1.82,-2)(1.83,-2)(1.84,-2)(1.85,-2)(1.86,-2)(1.87,-2)(1.88,-2)(1.89,-2)(1.9,-2)(1.91,-2)(1.92,-2)(1.93,-2)(1.94,-2)(1.95,-2)(1.96,-2)(1.97,-2)
(1.977,-2)
%(1.99,-2)
 %(2,-2) 
};

\addplot [
color=red!40!yellow,
solid,
only marks,
mark=square*,
mark size=5pt,
forget plot
]
coordinates{
(0.38,-2)(0.39,-2)(0.4,-2)(0.41,-2)(0.42,-2)(0.43,-2)(0.44,-2)(0.45,-2)(0.46,-2)(0.47,-2)(0.48,-2)(0.49,-2)(0.5,-2)(0.51,-2)(0.52,-2)(0.53,-2)(0.54,-2)(0.55,-2)(0.56,-2)(0.57,-2)(0.58,-2)
};

\addplot [
color=locol,
solid,
only marks,
mark=square*,
mark size=5pt,
forget plot
]
coordinates{
 (0.94,-2)(0.95,-2)(0.96,-2)(0.97,-2)(0.98,-2)(0.99,-2)(1,-2)(1.01,-2)(1.02,-2)(1.03,-2)(1.04,-2)(1.05,-2)(1.06,-2)(1.07,-2)(1.08,-2) 
};

\addplot [
color=green!90!black,
solid,
only marks,
mark=square*,
mark size=5pt,
forget plot
]
coordinates{
(0.023,-1.7)(0.03,-1.7)(0.04,-1.7)(0.05,-1.7)(0.06,-1.7)(0.07,-1.7)(0.08,-1.7)(0.09,-1.7)(0.10,-1.7)(0.11,-1.7)(0.12,-1.7)(0.13,-1.7)(0.14,-1.7)(0.15,-1.7)(0.16,-1.7)(0.17,-1.7)(0.18,-1.7)(0.19,-1.7)(0.20,-1.7)(0.21,-1.7)(0.22,-1.7)(0.23,-1.7)(0.24,-1.7)(0.25,-1.7)(0.26,-1.7)(0.27,-1.7)(0.28,-1.7)(0.29,-1.7)(0.30,-1.7)(0.31,-1.7)(0.32,-1.7)(0.33,-1.7)(0.34,-1.7)(0.35,-1.7)(0.36,-1.7)(0.37,-1.7)(0.38,-1.7)(0.39,-1.7)(0.40,-1.7)(0.41,-1.7)(0.42,-1.7)(0.43,-1.7)(0.44,-1.7)(0.45,-1.7)(0.46,-1.7)(0.47,-1.7)(0.48,-1.7)(0.49,-1.7)(0.50,-1.7)(0.51,-1.7)(0.52,-1.7)(0.53,-1.7)(0.54,-1.7)(0.55,-1.7)(0.56,-1.7)(0.57,-1.7)(0.58,-1.7)(0.59,-1.7)(0.60,-1.7)(0.61,-1.7)(0.62,-1.7)(0.63,-1.7)(0.64,-1.7)(0.65,-1.7)(0.66,-1.7)(0.67,-1.7)(0.68,-1.7)(0.69,-1.7)(0.70,-1.7)(0.71,-1.7)(0.72,-1.7)(0.73,-1.7)(0.74,-1.7)(0.75,-1.7)(1.56,-1.7)(1.57,-1.7)(1.58,-1.7)(1.59,-1.7)(1.60,-1.7)(1.61,-1.7)(1.62,-1.7)(1.63,-1.7)(1.64,-1.7)(1.65,-1.7)(1.66,-1.7)(1.67,-1.7)(1.68,-1.7)(1.69,-1.7)(1.70,-1.7)(1.71,-1.7)(1.72,-1.7)(1.73,-1.7)(1.74,-1.7)(1.75,-1.7)(1.76,-1.7)(1.77,-1.7)(1.78,-1.7)(1.79,-1.7)(1.80,-1.7)(1.81,-1.7)(1.82,-1.7)(1.83,-1.7)(1.84,-1.7)(1.85,-1.7)(1.86,-1.7)(1.87,-1.7)(1.88,-1.7)(1.89,-1.7)(1.90,-1.7)(1.91,-1.7)(1.92,-1.7)(1.93,-1.7)(1.94,-1.7)(1.95,-1.7)(1.96,-1.7)(1.97,-1.7)(1.977,-1.7)
};

\addplot [fill=red,draw=none,opacity=0.2,forget plot] coordinates{ (0,1.1)(0,1.9)(2,1.9)(2,1.1) };

%\addplot [
%color=black,
%dashed,
%line width=3pt,
%forget plot
%]
%coordinates{
% (0,3.825915)(2,3.825915)
%};
%
%\addplot [
%color=black,
%dashed,
%line width=3pt,
%forget plot
%]
%coordinates{
% (0,2.4975)(2,2.4975)
%};

\addplot [
color=red,
dashed,
line width=3pt,
forget plot
]
coordinates{
 (0,1.9)(2,1.9)
};

\addplot [
color=red,
dashed,
line width=3pt,
forget plot
]
coordinates{
 (0,1.1)(2,1.1)
};

\addplot [
color=black,
solid,
line width=2.5pt,
mark size=3pt,
mark=-,
forget plot
]
coordinates{
 (0.5,2.4902)(0.5,3.026)
};

\addplot [
color=black,
solid,
line width=2.5pt,
mark size=3pt,
mark=-,
forget plot
]
coordinates{
 (1.5,1.7052)(1.5,2.241)
};

\addplot [
color=black,
solid,
line width=2.5pt,
mark size=3pt,
mark=-,
forget plot
]
coordinates{
 (1,0.2645)(1,0.7996)
};

\addplot [
color=black,
solid,
line width=2.5pt,
mark size=3pt,
mark=-,
forget plot
]
coordinates{
 (0,-0.1683)(0,3.5848)
};

\addplot [
color=black,
solid,
line width=2.5pt,
mark size=3pt,
mark=-,
forget plot
]
coordinates{
 (2,-0.4448)(2,3.3083)
};

%\node at (axis cs:1.3, 3.1) [anchor=south west,minimum size=16pt] {\LARGE$\max\{\mu(\*x) + \beta \sigma(\*x)\}$};
%\node at (axis cs:0.7, 2.4) [anchor=south west,minimum size=16pt] {\LARGE$\max\{\mu(\*x) - \beta \sigma(\*x)\}$};

### 2013-07-31 figurefactory/files/voned_cl_41_poster.tex
Many small fixes

\addplot [
color=black,
solid,
line width=3pt,
mark=-,
mark size=4pt,
forget plot
]
coordinates{
 (1.23,0.0268)(1.23,1.9195)
};

\addplot [
color=yellow,
solid,
line width=5pt,
forget plot
]
coordinates{
 (1.23,1.2)(1.23,1.9195)
};

\addplot [
color=black,
solid,
line width=3pt,
mark=-,
mark size=4pt,
forget plot
]
coordinates{
 (0.23,0.9288)(0.23,3.8259)
};

\addplot [
color=yellow,
solid,
line width=5pt,
forget plot
]
coordinates{
 (0.23,0.9288)(0.23,1.2)
};

>>>>

\addplot [
color=black,
solid,
line width=2.5pt,
mark size=3pt,
mark=-,
forget plot
]
coordinates{
 (0.5,2.4902)(0.5,3.026)
};

\addplot [
color=black,
solid,
line width=2.5pt,
mark size=3pt,
mark=-,
forget plot
]
coordinates{
 (1.5,1.7052)(1.5,2.241)
};

\addplot [
color=black,
solid,
line width=2.5pt,
mark size=3pt,
mark=-,
forget plot
]
coordinates{
 (1,0.2645)(1,0.7996)
};

\addplot [
color=black,
solid,
line width=2.5pt,
mark size=3pt,
mark=-,
forget plot
]
coordinates{
 (0.005,-0.1683)(0.005,3.5848)
};

\addplot [
color=black,
solid,
line width=2.5pt,
mark size=3pt,
mark=-,
forget plot
]
coordinates{
 (1.997,-0.4448)(1.997,3.3083)
};

\node at (axis cs:0.4, 3) [anchor=south west,minimum size=16pt] {\Huge$Q(0.5)$};
\node at (axis cs:1.35, 2.3) [anchor=south west,minimum size=16pt] {\Huge$Q(1.5)$};
\node at (axis cs:0.88, -0.8) [anchor=south west,minimum size=16pt] {\Huge$Q(1)$};
\node at (axis cs:0.02, -0.8) [anchor=south west,minimum size=16pt] {\Huge$Q(0)$};
\node at (axis cs:1.72, -0.8) [anchor=south west,minimum size=16pt] {\Huge$Q(2)$};

### 2013-07-31 figurefactory/proof.tex
Many small fixes

\usepackage{libertine}

@@

 \node[st,below=3em of conv] (clas) {All points in $D$ have been classified}
   edge[pil] (conv);

@@

 \node[st,draw=none,below=3em of amb] (dummy) {};

 \node[st,left=2em of amb] (t0) {Monotonicity}
   edge[pil] (amb);
 \node[st,left=3em of dummy] (t1) {Samples ($t$)}
   edge[pil] (amb);
 \node[st,right=1em of t1] (t2) {Kernel ($k$)}
   edge[pil] (amb);
 \node[st,right=1em of t2] (t3) {Noise ($\sigma$)}
   edge[pil] (amb);
 \node[st,right=3em of t3,fill=col1] (t4) {$\beta_t$}
   edge[pil] (amb);

@@

 \node[st,below=3em of fit1] (gamma)
 {\makecell[c]
   {Quantify by max. information gain (Srinivas \emph{et al.}, 2010):\\[0.5em]
    $\gamma_t = \max_{\*y_t} I(\*y_{1:t}; f)$\\[0.5em]
    For SE kernel $\gamma_t \sim \mathcal{O}\left((\log t)^{d+1}\right)$
   }
 } edge[pil] (fit1);

@@

 \node[st,below=3em of acc] (loss) {$\max_{\*x\in D} \ell_h(\*x) \leq \epsilon$}
   edge[pil] (acc);

 \node[st,right=2em of loss] (rules) {Class. rules}
   edge[pil] (loss);

 \node[st,below=3em of loss] (est) {Correctly estimate $f$ w.h.p.}
   edge[pil] (loss);

 \node[st,right=2em of est] (delta) {$\delta$}
   edge[pil] (est);

 \node[st,below=3em of est] (large) {Conf. intervals are large enough}
   edge[pil] (est)
   edge[pil,<-] (t4);

>>>>

\usepackage{lmodern}

@@

 \node[st,below=2em of conv] (clas) {All points in $D$ have been classified}
   edge[pil] (conv);

@@

 \node[st,draw=none,below=2em of amb] (dummy) {};

 \node[st,left=1.5em of amb] (t0) {Monotonicity}
   edge[pil] (amb);
 \node[st,left=3em of dummy] (t1) {Samples ($t$)}
   edge[pil] (amb);
 \node[st,right=1em of t1] (t2) {Kernel ($k$)}
   edge[pil] (amb);
 \node[st,right=1em of t2] (t3) {Noise ($\sigma$)}
   edge[pil] (amb);
 \node[st,right=3em of t3,fill=col1] (t4) {$\beta_t$}
   edge[pil] (amb);

@@

 \node[st,below=2em of fit1] (gamma)
 {\makecell[c]
   {Quantify by max. information gain (Srinivas \emph{et al.}, 2010):\\[0.5em]
    $\gamma_t = \max_{\*y_t} I(\*y_{1:t}; f)$\\[0.5em]
    For SE kernel $\gamma_t \sim \mathcal{O}\left((\log t)^{d+1}\right)$
   }
 } edge[pil] (fit1);

@@

 \node[st,below=2em of acc] (loss) {$\max_{\*x\in D} \ell_h(\*x) \leq \epsilon$}
   edge[pil] (acc);

 \node[st,right=1.5em of loss] (rules) {Class. rules}
   edge[pil] (loss);

 \node[st,below=2em of loss] (est) {Correctly estimate $f$ w.h.p.}
   edge[pil] (loss);

 \node[st,right=1.5em of est] (delta) {$\delta$}
   edge[pil] (est);

 \node[st,below=2em of est] (large) {Conf. intervals are large enough}
   edge[pil] (est)
   edge[pil,<-] (t4);
